Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2017-10-27 paper/main.tex
Stage 1 reformat to ICLR format

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
\PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2017}

%\usepackage{nips_2017}
\usepackage[final]{nips_2017}
\bibliographystyle{abbrvnat}

% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage[final]{nips_2017}

@@

\providecommand{\scan}{\text{SCAN}}
\providecommand{\reduce}{\text{REDUCE}}
% declaration of the new block
\algblock{ParFor}{EndParFor}
% customising the new block
\algnewcommand\algorithmicparfor{\textbf{parfor}}
\algnewcommand\algorithmicpardo{\textbf{do}}
\algnewcommand\algorithmicendparfor{\textbf{end\ parfor}}
\algrenewtext{ParFor}[1]{\algorithmicparfor\ #1\ \algorithmicpardo}
\algrenewtext{EndParFor}{\algorithmicendparfor}

@@

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Eric Martin \\%\thanks{Use footnote for providing further
    %information about author (webpage, alternative
    %address)---\emph{not} for acknowledging funding agencies.} \\
  %Some Affiliation\\
  \texttt{eric@ericmart.in}
  %% examples of more authors
  \And
  Chris Cundy \\
  \texttt{c.cundy@berkeley.edu}
  %%\texttt{some@email.com}
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

@@

\subsubsection{Kernel performance}
We first illustrate the throughput advantage of the parallel scan algorithm for
evaluating the linear recurrence. For a minibatch comprised of \(b\) sequences
of length \(T\), we define the number of events as \(bT\) and the throughput as
the number of events per second. We implement two CUDA kernels, one which
evaluates the parallel linear recurrence described in algorithm \ref{alg:plr},
and one which evaluates the linear recurrence on GPU using the standard serial
approach (with parallelization over features but not sequence length).
This comparison is performed directly at the kernel level, avoiding
any overhead from TensorFlow. We find that the parallel kernel has
a distinct advantage at long sequence lengths with a speedup factor of up to 40x,
as shown in table \ref{table:kernel-throughput}.
At short sequence lengths, the parallel kernel does not perform well due to the
overhead of multiple passes over data and communication between processors.
\begin{table}
\begin{center}
  \begin{tabular}{@{}llll@{}}
    \label{table:kernel-throughput}
Sequence Length & \(m=4\)  & \(m=32\) & \(m=128\) \\ \midrule
16              & 0.06 & 0.06 & 0.05  \\
256             & 0.22 & 0.22 & 0.86  \\
4,096           & 1.02 & 2.94 & 3.36  \\
65,536          & 38.5 & 41.8 & 17.5  \\ \bottomrule
  \end{tabular}
\end{center}
\caption{
  Speedup of the parallel kernel compared to the serial kernel at various
  values of $(\text{minibatch size } \mathbf{x} \text{ features}) = m$.
  Performance was directly measured without any overhead from TensorFlow.
}
\end{table}

@@

%Future work can the development of parallel computable
%differentiable memory modules, and the combination of linear recurrence with
%convolutional sequence models.

% Besides future research, existing models such as
% Quasi-RNNs and strongly typed RNNs that already contain linear recurrences can
% immediately benefit from parallel linear recurrence. This work demonstrates the
% GILR-LSTM significantly accelerates the training of small to medium sized
% LSTMs. Although similar techniques have been used before, the now explicit
% concept of linear surrogacy provides a framework for future development and
% analysis of fast sequence models.

We intend to expand upon the experiments section and open-source the parallel
linear recurrence kernel in the near future.

>>>>

\documentclass{article}
\usepackage{iclr2018_conference,times}
\bibliographystyle{abbrvnat}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

\providecommand{\scan}{\text{SCAN}}
\providecommand{\reduce}{\text{REDUCE}}

% declaration of the new block
\algblock{ParFor}{EndParFor}
% customising the new block
\algnewcommand\algorithmicparfor{\textbf{parfor}}
\algnewcommand\algorithmicpardo{\textbf{do}}
\algnewcommand\algorithmicendparfor{\textbf{end\ parfor}}
\algrenewtext{ParFor}[1]{\algorithmicparfor\ #1\ \algorithmicpardo}
\algrenewtext{EndParFor}{\algorithmicendparfor}

@@

\author{Eric Martin \\
\texttt{eric@ericmart.in} \\
\And
Chris Cundy
Department of XX \\
University of XX \\
City, Country \\
\texttt{c.cundy@berkeley.edu} \\
}

\begin{document}
\maketitle

@@

\subsubsection{Kernel performance}
We first illustrate the throughput advantage of the parallel scan algorithm for
evaluating the linear recurrence. For a minibatch comprised of \(b\) sequences
of length \(T\), we define the number of events as \(bT\) and the throughput as
the number of events per second. We implement two CUDA kernels, one which
evaluates the parallel linear recurrence described in algorithm \ref{alg:plr},
and one which evaluates the linear recurrence on GPU using the standard serial
approach (with parallelization over features but not sequence length).
This comparison is performed directly at the kernel level, avoiding
any overhead from TensorFlow. We find that the parallel kernel has
a distinct advantage at long sequence lengths with a speedup factor of up to 40x,
as shown in table \ref{table:kernel-throughput}.
At short sequence lengths, the parallel kernel does not perform well due to the
overhead of multiple passes over data and communication between processors.
\begin{table}[t]
\caption{Parallel kernel speedup on $m$ features}
\begin{center}
\begin{tabular}{@{}llll@{}}
\label{table:kernel-throughput}
Sequence Length & \(m=4\)  & \(m=32\) & \(m=128\) \\ \midrule
16              & 0.06 & 0.06 & 0.05  \\
256             & 0.22 & 0.22 & 0.86  \\
4,096           & 1.02 & 2.94 & 3.36  \\
65,536          & 38.5 & 41.8 & 17.5  \\ \bottomrule
\end{tabular}
\end{center}
\end{table}

@@
